\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

% Set the page layout
\geometry{a4paper, margin=1in}

% Define custom title formatting
\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}

% Title and author information
\title{CRUD Operations of \\ CU Campus Event Management System}
\author{Your Name \\ University Name}
\date{\today}

\begin{document}

\maketitle

\tableofcontents
\newpage

\section{Introduction}
Provide an overview of the project and its purpose. Mention the goals and the technologies used, such as React, Node.js, and MySQL.

\section{Database Design}
\subsection{Schema Overview}
Describe the main tables and their relationships, including `Users`, `Events`, `Categories`, `Locations`, and so on.

\subsection{Entity-Relationship Diagram}
Include or reference an ER diagram showing the database design.

\section{CRUD Operations}
\subsection{Create}
Explain how users can create records, such as registering new users or creating events. Provide SQL examples.

\subsection{Read}
Discuss how users or administrators can retrieve data, such as viewing a list of events or participant details. Include SQL query examples.

\subsection{Update}
Describe how updates are handled, like modifying event details or user information. Include examples of SQL update statements.

\subsection{Delete}
Explain how deletions are managed, for instance, removing canceled events or deregistering users. Provide SQL examples.

\section{Frontend Integration}
Explain how the CRUD operations are integrated into the React frontend.

\subsection{Form Design}
Describe the forms used for input, such as event creation or user registration.

\subsection{API Endpoints}
Mention the Node.js endpoints for handling CRUD operations.

\section{Conclusion}
Summarize the system's functionality and future improvement plans.

\end{document}
